Maintenance Instructions

### 2025-01-11 MaintenanceInstructions.qmd
Wrapping up for the week

If your data looks at all like [Alix's](IndividualStudies/DataTables/AT_ChemicalCommunications_2025.csv){target="_blank"} or [Scotty's](IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply. Call the RankedOrderPlotStandard() and VolcanoPlotStandardized() functions to produce these plots with the same standardized formatting. On that note, you can alter the ggplot_styles.R file to change the standardized formatting.

>>>>

If your data looks at all like [Alix's](https://lipidinteractomicsrepository.netlify.app/individualstudies/at_2025){target="_blank"} or [Scotty's](https://lipidinteractomicsrepository.netlify.app/individualstudies/sf_2024){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply. Call the RankedOrderPlotStandard() and VolcanoPlotStandardized() functions to produce these plots with the same standardized formatting. On that note, you can alter the ggplot_styles.R file to change the standardized formatting.
